Bird beak's elaboration and exploration: data preparation

### 2021-09-10 Analysis/01-Data_preparation.Rmd
Update 01-Data_preparation.Rmd

## Selecting only the tips in the trait space
matching_tips <- consensus_tree$tip.label %in% rownames(shapespace)
consensus_tree <- drop.tip(consensus_tree, tip = consensus_tree$tip.label[!matching_tips])
```

>>>>

## Selecting only the tips in the trait space
clean.tree <- function(tree, space) {
    matching_tips <- tree$tip.label %in% rownames(space)
    return(drop.tip(tree, tip = tree$tip.label[!matching_tips]))
}
consensus_tree <- clean.tree(consensus_tree, shapespace)

## Reading the distribution of trees
trees_list <- read.tree("../Data/raw/Tree_data/AllBirdsHackett1.tre")
trees_list <- lapply(trees_list, clean.tree, shapespace)
class(trees_list) <- "multiPhylo"
save(trees_list, file = "../Data/Processed/trees_list.rda")
```
